Spike-and-Slab Generalized Additive Models and Scalable Algorithms for High-Dimensional Data

### 2022-02-11 Manuscript/R&R/00-response_letter.Rmd

---
output: 
  pdf_document:
    keep_tex: FALSE
    citation_package: biblatex
bibliography: reply_ref.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(targets)
tar_load(RR_path)
```

\newcommand{\tp}{*}

@@

\bigskip

# Response to Associate Editor
_Comments to the authors:_

_Please follow carefully the comments, criticisms and suggestions of the three referees._

__Response__: We summarize the major changes of our manuscript as a response to address the comments from the referees:
\begin{itemize}
    \item According to Reviewer \#2's and Reviewer \#4's comments, we modified the prior distribution of the non-linear effects inclusion indicator such that the strong hierarchy for bi-level selection is enforced. 
    \item According to Reviewer \#1's and Reviewer \#4's comments, we added linear lasso model and spikeSlabGAM model among the models to be compared. 
    \item According to Reviewer \#1's and Reviewer \#4's comments, we added a new set of simulation scenarios where the functions of predictors are linear.  
    \item According to Reviewer \#4's comment, we summarized the variable selection performance for all models of comparison and bi-level selection performance for the models that is capable, i.e. the proposed model and spikeSlabGAM.
    \item According to Reviewer \#4's comment, we recorded the computation performance of spikeSlabGAM.
    \item All existing figure and tables were updated to reflect the methodology change and simulation design change. Figures were added according to Reviewer \#4's comment.  [TODO: think what figures are needed]
    \item We fixed the additional typos and grammar errors according to Review \#2.The revision of the manuscript is marked in red [TODO: change this color to red]. Deletions are not highlighted.
\end{itemize}

### 2022-02-11 Manuscript/R&R/01-reviewer_1.Rmd
Added Changes

__Response__: We don't think any preliminary checkings or testings are necessary before implementing the proposed model, as long as some general rules of thumb for high-dimensional modeling are followed. Such rules of thumb includes .[Insert citaiton for ultra high-dimension thing, as the number of predictors is a function of the sample size.] As a supporting evidence, our added simulation demonstrates the proposed model performs well, in reference to the linear lasso model, even when signals are linear and sparse (see response to the Comment 1).

>>>>

__Response__: We don't think any preliminary checkings or testings are necessary before implementing the proposed model, as long as some general rules of thumb for high-dimensional modeling are followed. Such rules of thumb includes [TODO: Insert citaiton for ultra high-dimension thing, as the number of predictors is a function of the sample size.]. As a supporting evidence, our added simulation demonstrates the proposed model performs well, in reference to the linear lasso model, even when signals are linear and sparse (see response to the Comment 1).

### 2022-02-11 Manuscript/R&R/02-reviewer_2.Rmd
Added Changes

>>>>

__Response__: Thank you for the comment. We changed the prior distribution of the non-linear effects inclusion indicator to be $\gamma^\tp|\gamma, \theta \sim Bin(1, \gamma\theta)$ (See Equation ([TODO: add the equation number])), in comparison to $\gamma^\tp| \theta \sim Bin(1, \theta)$ previously. This prior formulation is motivated by effect forcing discussed in (Chipman, 2004). Now, the inclusion of the nonlinear effects is strictly dependent on the inclusion of the linear effects, and hence, reflects the hierarchy of bi-level selection. The modification of the prior doesn't complicate the model fitting algorithm. The $\gamma$ can be analytically integrated out of the density function (See Equation ([TODO: add the equation number]) and appendix) and requires minimum change of the proposed algorithms. In other words, the proposed model remain feasible for high-dimensional data analysis and retains the claimed computational advantages.
